Navigating to a Greener Europe through Clean Electricity Procurement

### 2023-04-04 manuscript/manuscript.tex
final LaTeX configs, move auxiliaries to gitignore
manuscript skeleton

\documentclass[11pt, 5p]{elsarticle}

@@

\graphicspath{{../results/graphics/},}

@@

% acronyms
\makeglossaries
\newacronym{tes}{TES}{Thermal energy storage (in form of water tanks)}
\newacronym{chp}{CHP}{Combined heat and power plant}
\newacronym{cop}{COP}{Coefficient of Performance}
\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
\newacronym{PV}{PV}{Solar photovoltaics}
\newacronym{ghg}{GHG}{Greenhouse gas}
\newacronym{EU}{EU}{European Union}
\newacronym{dea}{DEA}{Danish Energy Agency}
\newacronym{helmeth}{HELMETH}{Integrated High-Temperature Electrolysis and Methanation for Effective Power to Gas Conversion}
\newacronym{jrc}{JRC}{Joint Research Center}
\newacronym{ocgt}{OCGT}{Open cyclic gas turbine}
\newacronym{v2g}{V2G}{Vehicle to Grid}
\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
\newacronym{tyndp}{TYNDP}{Ten-year network development plan}
\newacronym{entso-e}{ENTSO-E}{European network for transmission system operators electricity}
\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
\newacronym{covid}{COVID-19}{Coronavirus disease 2019}
\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
\newacronym{dsm}{DSM}{Demand side management}
\newacronym{hvdc}{HVDC}{High voltage direct current}
\newacronym{phs}{PHS}{Pumped hydro storage}
\newacronym{dac}{DAC}{Direct air capture}
\newacronym{sng}{SNG}{Synthetic natural gas}
\newacronym{fom}{FOM}{Fixed operation and maintenance costs}
\newacronym{vom}{VOM}{Variable operation and maintenance costs}
\newacronym{ppa}{PPA}{Power Purchase Agreement}
\newacronym{ptc}{PTC}{Production Tax Credit}
\newacronym{res}{RES}{Renewable energy sources}
\newacronym{necp}{NECP}{National energy climate plan}
\newacronym{ets}{ETS}{Emissions Trading System}
\newacronym{capex}{CAPEX}{Capital expenditures}
\newacronym{cfd}{CfD}{Contract for Difference}
\newacronym{cfe}{CFE}{Carbon-free electricity}

@@

	\title{ new paper}

	\author[affil]{ iegor } % \corref{correspondingauthor}
	\ead{ name@box }

	\address[affil]{ affiliation }

@@

\section{Methods}
\label{sec:methods}

\input{sections/methods.tex}

\section{Results}
\label{sec:results}

\input{sections/results.tex}

\section{Discussion}
\label{sec:discussion}

\input{sections/discussion.tex}

\section{Conclusion}
\label{sec:conclusion}

\input{sections/conclusion.tex}

@@

% XY gratefully acknowledge funding from XY under grant no. 00000.

\section*{License}
% \doclicenseLongText
% \doclicenseIcon

@@

\textbf{Author XY}:
Conceptualization --
Data curation --
Formal Analysis --
Funding acquisition --
Investigation --
Methodology --
Project administration --
Resources --
Software --
Supervision --
Validation --
Visualization --
Writing - original draft --
Writing - review \& editing

@@

\section*{Abbreviations}
\printglossary[type=\acronymtype]

>>>>

\documentclass[11pt, 5p, nopreprintline]{elsarticle}

@@

\graphicspath{{../results/paper/},}

@@

% acronyms
\makeglossaries
\newacronym{tes}{TES}{Thermal Energy Storage (in form of water tanks)}
\newacronym{chp}{CHP}{Combined Heat and Power plant}
\newacronym{cop}{COP}{Coefficient of Performance}
\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
\newacronym{PV}{PV}{Solar photovoltaics}
\newacronym{ghg}{GHG}{Greenhouse gas}
\newacronym{EU}{EU}{European Union}
\newacronym{dea}{DEA}{Danish Energy Agency}
\newacronym{helmeth}{HELMETH}{Integrated High-Temperature Electrolysis and Methanation for Effective Power to Gas Conversion}
\newacronym{jrc}{JRC}{Joint Research Center}
\newacronym{ocgt}{OCGT}{Open Cycle Gas Turbine}
\newacronym{v2g}{V2G}{Vehicle to Grid}
\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{hvdc}{HVDC}{High Voltage Direct Current}
\newacronym{phs}{PHS}{Pumped Hydro Storage}
\newacronym{dac}{DAC}{Direct Air Capture}
\newacronym{sng}{SNG}{Synthetic Natural Gas}
\newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
\newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
\newacronym{ppa}{PPA}{Power Purchase Agreement}
\newacronym{ptc}{PTC}{Production Tax Credit}
\newacronym{res}{RES}{Renewable Energy Sources}
\newacronym{necp}{NECP}{National Energy and Climate Plan}
\newacronym{ets}{ETS}{Emissions Trading System}
\newacronym{capex}{CAPEX}{Capital expenditures}
\newacronym{cfd}{CfD}{Contract for Difference}
\newacronym{cfe}{CFE}{Carbon-Free Electricity}
\newacronym{ci}{CI}{Corporate and Industry sectors}

@@

	\title{Navigating to a Greener Europe through Clean Electricity Procurement}

	\author[tubaddress]{Iegor Riepin}
	\ead{iegor.riepin@tu-berlin.de}
	\author[tubaddress]{Tom Brown} 
	\ead{t.brown@tu-berlin.de}

	\address[tubaddress]{Department of Digital Transformation in Energy Systems, TU Berlin, Germany}

@@

\section{Methods}
\label{sec:methods}
\input{sections/methods.tex}

\section{Results}
\label{sec:results}
\input{sections/results.tex}

\section{Discussion}
\label{sec:discussion}
\input{sections/discussion.tex}

\section{Conclusion}
\label{sec:conclusion}
\input{sections/conclusion.tex}

@@

This paper is an independent project, which is based on the third-party funded 
research work \cite{Riepin-report-2022}. This research work was supported by a grant from Google Inc.

@@

\textbf{Iegor Riepin}:
Conceptualization --
Data curation --
Formal Analysis --
Investigation --
Methodology --
Software --
Validation --
Visualization --
Writing - original draft

\textbf{Tom Brown}:
Conceptualization --
Methodology --
Software --
Supervision --
Writing - review \& editing

@@

\printglossary[type=\acronymtype]
